Generating function solution for the bursty unregulated promoter

### 2020-01-28 doc/theorists_notebook/20191218gen_fcn_unreg.tex
Extended constit FISH analysis with theory interpretation

F(z, t) &=  \left(\frac{1-(1+(z-1)e^{-t})(1-\theta)}{1-z(1-\theta)}\right)^{\lambda}

@@

>>>>

F(z, t) &=  \left(\frac{1-(1-\theta)(1+(z-1)e^{-t})}
                        {1-(1-\theta)z}\right)^{\lambda}

@@

\mmnote{Our t-dependence is already different than theirs, even though
the steady state is the same. For trivial $k=0$ IC, everything will work
out similarly, I think. For anything else, I think the direct approach
of differentiating will produce an impossible mess. But we might be able
to use their idea of a ``propagator'' probability and do a convolution
over that; in principle, getting to the same place, but that might be
tidier??}
